This appendix is a technical staging area for the operator layer referenced in
\texttt{definitions.tex}, \texttt{spectral-framework.tex}, and
\texttt{proof-architecture.tex}. It records the current best formalization
attempt without claiming that a complete operator construction has been achieved.

\auditnote{Everything in this appendix is provisional unless explicitly linked
to an established statement in the main text. In particular, it should be read
as interface design for mathematical audit, not as a completed construction.}

\subsection{Intended ambient space}

The manuscript-level symbol $H$ currently denotes a \emph{proposed spectral
object} (Section~7, \texttt{spectral-framework.tex}), not yet a finalized
single self-adjoint operator. A concrete construction path should specify:
\begin{enumerate}
  \item a complex Hilbert space $(\mathcal{H},\langle\cdot,\cdot\rangle)$,
  \item a dense subspace $\mathcal{D}_0\subset\mathcal{H}$ used for initial
  definition,
  \item a linear action rule on $\mathcal{D}_0$,
  \item a closure or extension procedure yielding the operative domain
  $\mathcal{D}(H)$.
\end{enumerate}

A useful baseline is to keep two candidate ambient classes under review:
\begin{itemize}
  \item \textbf{Mellin/Fourier class:} function spaces where multiplicative
  structure and transforms tied to zeta-side expressions are naturally typed.
  \item \textbf{Hardy-type class:} analytic-function spaces where reflection and
  boundary-value symmetries may be easier to formulate.
\end{itemize}

\openbridge{The manuscript has not yet fixed a unique ambient space with full
proof-level consequences for all later stages. Choosing one class requires
re-checking every downstream hypothesis in Stages 2--6 of
\texttt{proof-architecture.tex}.}

\subsection{Candidate domain requirements}

Any finalized domain $\mathcal{D}(H)$ should be specified by verifiable
conditions, not only by intention. The current minimum checklist is:
\begin{enumerate}
  \item \textbf{Density and typing:} $\mathcal{D}(H)$ is dense in
  $\mathcal{H}$; $H\colon\mathcal{D}(H)\to\mathcal{H}$ is well-defined.
  \item \textbf{Regularity/decay package:} explicit growth, decay, and
  differentiability/integrability assumptions sufficient for every integral or
  transform used later in the balance functional.
  \item \textbf{Closure control:} a stated route to closability and an explicit
  statement of whether the argument uses symmetry, essential self-adjointness,
  or only weaker graph properties.
  \item \textbf{Spectral meaning requirement:} a precise declaration of which
  spectral statements are actually needed (e.g., resolvent bounds, spectral
  measure statements, semigroup control), rather than a blanket requirement for
  full spectral theorem machinery.
\end{enumerate}

\openbridge{At present, no complete theorem in the manuscript verifies this full
checklist for a single candidate $H$. This gap is consistent with the open items
in Section~10 (\texttt{limitations.tex}).}

\subsection{Symmetry-compatibility requirements}

The operator layer must interface with the classical involutions fixed in
\texttt{definitions.tex} and \texttt{symmetry-framework.tex}, notably
\(s\mapsto 1-s\) and \(s\mapsto \bar s\). A candidate construction should
include:
\begin{enumerate}
  \item an explicit reflection/conjugation action on $\mathcal{H}$ (or on a
  related representation space),
  \item a compatibility identity showing how $H$ transforms under these actions,
  \item a domain-invariance statement (or a controlled defect term) under the
  same symmetries,
  \item a statement connecting this compatibility to the balance criterion used
  in Section~7.
\end{enumerate}

\openbridge{No completed theorem currently proves that the proposed balance map
is symmetry-compatible on a fully specified admissible class. This remains tied
to placeholder lemmas in \texttt{lemmas.tex} (B2/B3 block).}

\subsection{Balance-functional interface requirements}

Section~7 requires a functional $\Phi$ extracted from the operator layer. The
interface should be written as explicit data:
\[
(\mathcal{H},\mathcal{D}(H),H;\ \mathcal{A},\Phi),
\]
where $\mathcal{A}\subseteq\C$ is the admissible class from
\texttt{definitions.tex}. For auditability, the manuscript needs:
\begin{enumerate}
  \item \textbf{Definition-level typing:}
  \(\Phi\colon\mathcal{A}\to\R\) or \(\Phi\colon\mathcal{A}\to\C\)
  with the exact codomain fixed.
  \item \textbf{Well-posedness theorem target:} a lemma proving finiteness and
  determinacy of $\Phi(s)$ for all $s\in\mathcal{A}$ under explicit
  assumptions.
  \item \textbf{Stability target:} a perturbation statement identifying which
  data deformations preserve admissibility and preserve/quantify changes in
  $\Phi$.
  \item \textbf{Zero-interface target:} a theorem-level rule connecting
  ``balanced'' states (as defined via $\Phi$) to encoded zeta-side points,
  including exclusion of spurious balanced states.
\end{enumerate}

\openbridge{Items (2)--(4) are not yet proved in finalized form. They correspond
exactly to unresolved dependencies stated in Sections~5 and~8.}

\subsection{Unresolved operator choices (explicitly open)}

The following choices remain open design decisions. None should be read as
settled.
\begin{enumerate}
  \item \textbf{Single operator vs.\ operator family.} Whether the framework
  should use one closed operator $H$ or a parameterized family
  $\{H_\theta\}_{\theta\in\Theta}$ with a derived aggregate functional.
  \item \textbf{Self-adjoint route vs.\ weaker route.} Whether later stages
  truly require self-adjointness, or only symmetry plus additional coercive
  estimates sufficient for the balance/exclusion arguments.
  \item \textbf{Trace-formula dependence.} Whether the architecture relies on an
  explicit trace identity, or only on local spectral/transform relations.
  \item \textbf{Admissible-class geometry.} Whether
  $\mathcal{A}\subset\C$ is best specified by analytic continuation,
  transform-side decay, or mixed constraints. Different choices may alter the
  burden of Target~A and Target~B.
\end{enumerate}

\placeholder{Resolution of these choices should be recorded in the main sections
(Definitions, Spectral Framework, Proof Architecture, Limitations) and then
back-propagated here as a versioned operator specification.}

\subsection{Audit-use guidance}

Advanced readers can use this appendix as a checklist when reviewing operator
claims in the manuscript:
\begin{itemize}
  \item Is every operator claim explicitly tagged as established theorem,
  provisional requirement, or open bridge?
  \item Are admissibility and balance statements stated with full hypothesis
  packages and domain/codomain typing?
  \item Do symmetry-compatibility statements identify the precise action on
  operator data, not only on complex-plane points?
  \item Is each claimed implication traceable to a lemma/theorem target in
  \texttt{proof-architecture.tex} and \texttt{lemmas.tex}?
\end{itemize}

\auditnote{Until the operator choices in B.5 are resolved and proved, this
appendix should be interpreted as a concrete map of obligations, not as a
completed operator model.}
