This section records the manuscript's conditional reduction step in explicit dependency form.
The purpose is to isolate the final logical deduction from the earlier bridges that still require proof.

\subsection*{Conditional reduction statement}
\begin{proposition}[Framework-internal conditional RH reduction]
Assume the manuscript definitions of the state space $H$, admissibility class, and balance criterion are fixed and well-posed under a hypothesis package $\mathcal{A}$.
Assume further that the following three inputs hold under the same $\mathcal{A}$:
\begin{enumerate}
  \item \textbf{Target A (zero--balance correspondence).} Every nontrivial zero in the critical strip corresponds to a balanced point in the admissible class (with converse direction as specified in the correspondence theorem).
  \item \textbf{Target B (critical-line localization of balanced points).} Every admissible balanced point satisfies $\RePart(s)=\tfrac12$.
  \item \textbf{Global off-line exclusion package.} No admissible off-line balanced configuration exists in the full critical strip, including boundary/degenerate regimes required by the framework's parameterization.
\end{enumerate}
Then every nontrivial zero $\rho$ of $\zeta$ satisfies $\RePart(\rho)=\tfrac12$.
\end{proposition}

\subsection*{Separation of burdens: local uniqueness vs global exclusion}
For audit clarity, the manuscript treats two logically distinct obligations.
\begin{enumerate}
  \item \textbf{Local uniqueness-of-balance burden (Target B core).}
  Prove that in a specified regime $\mathcal{R}_{\mathrm{loc}}\subseteq\mathcal{A}$, balance implies $\RePart(s)=\tfrac12$.
  This is a localization statement.
  \item \textbf{Global off-line exclusion burden (Stage 6 core).}
  Prove that no admissible balanced point with $\RePart(s)\neq\tfrac12$ exists anywhere in the full strip region of interest, including non-perturbative, boundary-near, and large-parameter regimes not automatically covered by $\mathcal{R}_{\mathrm{loc}}$.
\end{enumerate}
The second item is not a restatement of the first.
It is an extension/closure problem requiring additional uniform control.


\subsection*{Minimum synchronized hypothesis package for the preferred Stage~6 route (formulation target only)}
\label{subsec:min-stage6-package}
To state the preferred Stage~6 theorem target in a single non-ambiguous form, we isolate a minimum synchronized package
\[
\mathcal{H}_{\mathrm{S6}}^{\min}
\]
for the route
\[
\text{local uniqueness on }\mathcal{R}_{\mathrm{loc}}\Longrightarrow\text{transfer on }\mathcal{A}_{\mathrm{strip}}\Longrightarrow\text{no-alternative-locus}\Longrightarrow\text{full-strip exclusion}.
\]
This package is a \emph{formulation scaffold}.
It is not presented as sufficient for a proof.
It is not presented as proved.

\paragraph{Minimum items required to state the preferred route as a theorem target.}
Let
\[
\mathcal{A}_{\mathrm{strip}}:=\{s\in\mathcal{A}:0<\RePart(s)<1\},\qquad
\mathcal{B}:=\{s\in\mathcal{A}_{\mathrm{strip}}:\Phi_H(s)=0\},\qquad
\mathcal{R}_{\mathrm{loc}}\subseteq\mathcal{A}_{\mathrm{strip}}.
\]
The synchronized minimum package $\mathcal{H}_{\mathrm{S6}}^{\min}$ consists of:
\begin{enumerate}
  \item \textbf{(S6-M1) Admissibility synchronization and stability.}
  One admissible class $\mathcal{A}$ is used across Target~A, Stage~5 local uniqueness, transfer, and Stage~6 exclusion, with explicit local-to-global admissibility stability from $\mathcal{R}_{\mathrm{loc}}$ to $\mathcal{A}_{\mathrm{strip}}$.
  \item \textbf{(S6-M2) Balance-functional well-posedness on the full strip class.}
  $\Phi_H(s)$ is theorem-level well-defined on every $s\in\mathcal{A}_{\mathrm{strip}}$ used by transfer/no-alternative-locus statements, with no regime change in predicate meaning between local and global steps.
  \item \textbf{(S6-M3) Symmetry compatibility without hypothesis loss.}
  Reflection/conjugation transport preserves the admissibility and regularity assumptions used in the same theorem package.
  \item \textbf{(S6-M4) Operator-side structural control actually used by Stage~6.}
  Only the operator-side assumptions needed for transfer/exclusion are included (in current manuscript notation, OP7--OP8 plus their OP1--OP6 prerequisites where invoked).
  No finalized operator realization is assumed here beyond this explicit interface requirement.
  \item \textbf{(S6-M5) Analytic-control package required by transfer.}
  Strip-wide continuation/compactness/uniformity and interchange legitimacy assumptions are declared at the level needed to pass from local Stage-5 control to global strip statements (AC1--AC6 in current notation).
  \item \textbf{(S6-M6) No-hidden-off-line-branch / no-alternative-locus input.}
  The theorem input explicitly excludes creation or persistence of off-line connected components of $\mathcal{B}$ outside $\mathcal{R}_{\mathrm{loc}}$ under the same synchronized assumptions.
  \item \textbf{(S6-M7) Contradiction-route compatibility clause.}
  Any assumed off-line balanced point $s_\ast\in\mathcal{A}_{\mathrm{strip}}$ with $\RePart(s_\ast)\neq\tfrac12$ is interpreted under exactly the same package $\mathcal{H}_{\mathrm{S6}}^{\min}$ (no hypothesis switching between premise and exclusion step).
\end{enumerate}

\paragraph{Theorem target that $\mathcal{H}_{\mathrm{S6}}^{\min}$ is intended to formulate.}
Under $\mathcal{H}_{\mathrm{S6}}^{\min}$, the preferred Stage~6 target is the clean conditional implication
\[
\Big(\forall s\in\mathcal{B}\cap\mathcal{R}_{\mathrm{loc}},\ \RePart(s)=\tfrac12\Big)\Longrightarrow\Big(\forall s\in\mathcal{B}\cap\mathcal{A}_{\mathrm{strip}},\ \RePart(s)=\tfrac12\Big),
\]
together with explicit no-alternative-locus interpretation on $\mathcal{A}_{\mathrm{strip}}$.
In this manuscript version, this remains a theorem target only.

\begin{drafttheorem}[Master Stage~6 exclusion theorem target under $\mathcal{H}_{\mathrm{S6}}^{\min}$]
\label{thm:stage6-master-exclusion-target}
\placeholder{Theorem target under construction; proof not yet provided.}
Let
\[
\mathcal{A}_{\mathrm{strip}}:=\{s\in\mathcal{A}:0<\RePart(s)<1\},\qquad
\mathcal{B}:=\{s\in\mathcal{A}_{\mathrm{strip}}:\Phi_H(s)=0\},\qquad
\mathcal{R}_{\mathrm{loc}}\subseteq\mathcal{A}_{\mathrm{strip}}.
\]
Under the synchronized minimum package $\mathcal{H}_{\mathrm{S6}}^{\min}$, the preferred Stage~6 route aims to establish the transfer statement
\[
\Big(\forall s\in\mathcal{B}\cap\mathcal{R}_{\mathrm{loc}},\ \RePart(s)=\tfrac12\Big)
\Longrightarrow
\Big(\forall s\in\mathcal{B}\cap\mathcal{A}_{\mathrm{strip}},\ \RePart(s)=\tfrac12\Big),
\]
and records the following theorem-target-equivalent formulations under the same package:
\begin{enumerate}
  \item \textbf{Pointwise form:} every admissible balanced point in $\mathcal{A}_{\mathrm{strip}}$ lies on $\RePart(s)=\tfrac12$.
  \item \textbf{Set-theoretic form:}
  \[
  \mathcal{B}\subseteq\{s\in\mathcal{A}_{\mathrm{strip}}:\RePart(s)=\tfrac12\},
  \]
  equivalently
  \[
  \mathcal{B}\cap\{s\in\mathcal{A}_{\mathrm{strip}}:\RePart(s)\neq\tfrac12\}=\varnothing.
  \]
  \item \textbf{Component/locus form:} no connected component of $\mathcal{B}$ is off the critical line.
  \item \textbf{Contradiction-style form:} assuming an admissible off-line balanced point
  \[
  s_\ast\in\mathcal{B}\cap\mathcal{A}_{\mathrm{strip}},\qquad \RePart(s_\ast)\neq\tfrac12,
  \]
  must contradict at least one ingredient of the same synchronized package $\mathcal{H}_{\mathrm{S6}}^{\min}$.
\end{enumerate}
This theorem is the current single master Stage~6 target under audit.
The list above is a statement-level alignment device, not an independent proof of equivalence.
It is a formulation target only in this manuscript version and is not proved.
\end{drafttheorem}

\subsection*{Audit list: preferred equivalent formulations of the Stage~6 endpoint}
For cross-checking across sections, we summarize the preferred forms of
\cref{thm:stage6-master-exclusion-target} under $\mathcal{H}_{\mathrm{S6}}^{\min}$:
\begin{enumerate}
  \item \textbf{Transfer form (route statement):}
  \[
  \Big(\forall s\in\mathcal{B}\cap\mathcal{R}_{\mathrm{loc}},\ \RePart(s)=\tfrac12\Big)
  \Longrightarrow
  \Big(\forall s\in\mathcal{B}\cap\mathcal{A}_{\mathrm{strip}},\ \RePart(s)=\tfrac12\Big).
  \]
  \item \textbf{Pointwise exclusion form:}
  \[
  \forall s\in\mathcal{B}\cap\mathcal{A}_{\mathrm{strip}},\quad \RePart(s)=\tfrac12.
  \]
  \item \textbf{Set-theoretic form:}
  \[
  \mathcal{B}\cap\{s\in\mathcal{A}_{\mathrm{strip}}:\RePart(s)\neq\tfrac12\}=\varnothing.
  \]
  \item \textbf{Component/locus form:} no off-line connected component of $\mathcal{B}$ exists in $\mathcal{A}_{\mathrm{strip}}$.
  \item \textbf{Contradiction form:} any assumed admissible off-line balanced point contradicts at least one clause of $\mathcal{H}_{\mathrm{S6}}^{\min}$.
\end{enumerate}
In this manuscript version, this list is recorded for audit readability only.
It does not assert that these formulations have been proved equivalent outside the stated theorem-target framing under $\mathcal{H}_{\mathrm{S6}}^{\min}$.

\paragraph{Minimum structural requirements versus stronger optional assumptions.}
The package $\mathcal{H}_{\mathrm{S6}}^{\min}$ is intentionally limited to assumptions required to \emph{state} the preferred route coherently.
Stronger hypotheses (for example stronger coercive gaps, stronger positivity monotonicity statements, or model-specific rigidity beyond what is needed to formulate transfer/no-alternative-locus) are treated as optional strengthening packages for proving the route, not as part of the minimum statement scaffold.

\subsection*{Local-to-global transfer principle for \texorpdfstring{$\mathcal{B}$}{B} (open theorem target)}
This subsection isolates the missing closure bridge between Stage~5 local uniqueness and Stage~6 full-strip exclusion.
It is recorded as a theorem target only.
It is a sub-burden intended to discharge the master target \cref{thm:stage6-master-exclusion-target}.

\paragraph{Local versus global in the present manuscript.}
Write
\[
\mathcal{B}:=\{s\in\mathcal{A}_{\mathrm{strip}}:\Phi_H(s)=0\},\qquad
\mathcal{A}_{\mathrm{strip}}:=\{s\in\mathcal{A}:0<\RePart(s)<1\}.
\]
``Local'' means the declared Stage-5 regime $\mathcal{R}_{\mathrm{loc}}\subseteq\mathcal{A}_{\mathrm{strip}}$ where uniqueness estimates are assumed/proved.
``Global'' means the full admissible strip class $\mathcal{A}_{\mathrm{strip}}$, including boundary-near, non-perturbative, and large-parameter sectors not automatically covered by $\mathcal{R}_{\mathrm{loc}}$.

\paragraph{Transfer theorem target (closure bridge; not proved).}
The needed bridge can be stated in the following audit form:
\begin{quote}
Under a synchronized hypothesis package $\mathcal{H}_{\mathrm{tr}}$, if Stage-5 local uniqueness holds on $\mathcal{R}_{\mathrm{loc}}$, then every $s\in\mathcal{B}\cap\mathcal{A}_{\mathrm{strip}}$ satisfies $\RePart(s)=\tfrac12$.
\end{quote}
Equivalently, under $\mathcal{H}_{\mathrm{tr}}$ there is no off-line connected component of $\mathcal{B}$ that is disjoint from the local regime where uniqueness is established.

\begin{drafttheorem}[Local-to-global transfer principle target for $\mathcal{B}$ (Stage~6 bridge)]
\label{thm:transfer-target-B}
\placeholder{Theorem target under construction; proof not yet provided.}
Let
\[
\mathcal{B}:=\{s\in\mathcal{A}_{\mathrm{strip}}:\Phi_H(s)=0\},
\qquad
\mathcal{A}_{\mathrm{strip}}:=\{s\in\mathcal{A}:0<\RePart(s)<1\},
\]
and let $\mathcal{R}_{\mathrm{loc}}\subseteq\mathcal{A}_{\mathrm{strip}}$ denote the Stage-5 local regime.
The required closure bridge is a theorem target of the form:
\[
\Big(\forall s\in\mathcal{B}\cap\mathcal{R}_{\mathrm{loc}},\ \RePart(s)=\tfrac12\Big)
\Longrightarrow
\Big(\forall s\in\mathcal{B},\ \RePart(s)=\tfrac12\Big),
\]
under one synchronized hypothesis package $\mathcal{H}_{\mathrm{tr}}$.
The package must include, at minimum:
\begin{enumerate}
  \item admissibility stability from local to global regimes;
  \item compatibility of Stage-5 local estimates with the full admissible strip class;
  \item continuation/compactness/uniformity control across boundary-near, non-perturbative, and large-parameter sectors;
  \item no-loss symmetry compatibility under reflection/conjugation transport;
  \item exclusion of new off-line connected components of $\mathcal{B}$ arising only outside $\mathcal{R}_{\mathrm{loc}}$.
\end{enumerate}
This theorem target is the explicit bridge between local Target~B control and full-strip off-line exclusion.
It is not established in the current manuscript version.
\end{drafttheorem}

\subsection*{First executable Stage~6 theorem target under audit: contradiction-ready admissibility-stability transfer}
The manuscript now fixes one \emph{first proving target} inside Stage~6 in contradiction-ready form.
This is the first theorem-sized burden to discharge under the preferred route.
It is not proved in this manuscript version.

\begin{drafttheorem}[Draft first Stage~6 subtheorem target (contradiction form): admissibility-stability transfer exclusion]
\label{thm:stage6-first-subtarget-admissibility}
\placeholder{Draft theorem target under construction; proof not yet provided.}
Assume the synchronized minimum package $\mathcal{H}_{\mathrm{S6}}^{\min}$, and write
\[
\mathcal{A}_{\mathrm{strip}}:=\{s\in\mathcal{A}:0<\RePart(s)<1\},\qquad
\mathcal{B}:=\{s\in\mathcal{A}_{\mathrm{strip}}:\Phi_H(s)=0\},\qquad
\mathcal{R}_{\mathrm{loc}}\subseteq\mathcal{A}_{\mathrm{strip}}.
\]
Let $\mathfrak{C}_{\mathrm{tr}}$ denote the transfer class (paths/chains/families, according to the eventual model) used to transport Stage-5 local hypotheses from $\mathcal{R}_{\mathrm{loc}}$ into $\mathcal{A}_{\mathrm{strip}}$.

\paragraph{Contradiction-ready theorem target (statement form only).}
The first Stage~6 proving attempt is to establish the following implication under one fixed hypothesis package, with no hypothesis switching.
\begin{enumerate}
  \item \textbf{Ambient regime and synchronized package.}
  Work only in $\mathcal{A}_{\mathrm{strip}}$ under the single package $\mathcal{H}_{\mathrm{S6}}^{\min}$, using the same admissibility and balance predicates in local, transfer, and contradiction steps.

  \item \textbf{Contradiction assumption package.}
  Assume there exists a transfer-reachable endpoint $s_\ast\in\mathcal{A}_{\mathrm{strip}}$ such that
  \[
  s_\ast\in\mathcal{B},\qquad \RePart(s_\ast)\neq\tfrac12,
  \]
  and there exists $C_\ast\in\mathfrak{C}_{\mathrm{tr}}$ joining a local anchor point in $\mathcal{R}_{\mathrm{loc}}$ to $s_\ast$.

  \item \textbf{Balance and transport assumptions attached to the contradiction premise.}
  Assume $\Phi_H(s_\ast)=0$ and assume that along $C_\ast$ the exact Stage-5 local hypothesis tuple used for local uniqueness is transported without loss (admissibility clauses, well-posedness clauses, symmetry-compatibility clauses, and regularity clauses required by that local uniqueness statement).

  \item \textbf{Intermediate support burden (explicit open bridge).}
  Prove, as a separate lemma-level bridge, that the transport assertion in item~(3) is theorem-usable for every transfer-reachable endpoint: continuation along each relevant $C\in\mathfrak{C}_{\mathrm{tr}}$ preserves the same Stage-5 hypothesis tuple with no drift between local and endpoint predicates.

  \item \textbf{Target contradiction conclusion for this first subtheorem.}
  Under items~(1)--(4), derive incompatibility with the transported Stage-5 local uniqueness clause at $s_\ast$.
  Equivalently, conclude that no transfer-reachable off-line balanced point exists under $\mathcal{H}_{\mathrm{S6}}^{\min}$.
\end{enumerate}
Equivalent exclusion form for this first subtarget:
\[
\mathcal{B}_{\mathrm{tr}}\cap\{s\in\mathcal{A}_{\mathrm{strip}}:\RePart(s)\neq\tfrac12\}=\varnothing,
\]
where
\[
\mathcal{B}_{\mathrm{tr}}:=\{s\in\mathcal{B}: \text{$s$ is reachable from $\mathcal{R}_{\mathrm{loc}}$ by some }C\in\mathfrak{C}_{\mathrm{tr}}\}.
\]
This is the first executable exclusion target only for the transfer-reachable class $\mathcal{B}_{\mathrm{tr}}$.
It is not yet the full Stage~6 endpoint on all of $\mathcal{B}$.
\paragraph{Status and scope boundary.}
The theorem above is a sharpened contradiction-ready target under audit.
It is not a proved theorem.
It does not assume a finalized operator realization beyond the declared OP/AC interface inside $\mathcal{H}_{\mathrm{S6}}^{\min}$.
\paragraph{Relation to the master Stage~6 target.}
\cref{thm:stage6-first-subtarget-admissibility} is not the Stage~6 endpoint.
It is the first dependency in the preferred chain toward \cref{thm:stage6-master-exclusion-target}.
Without this contradiction-ready transfer exclusion target, the transfer implication
\[
\Big(\forall s\in\mathcal{B}\cap\mathcal{R}_{\mathrm{loc}},\ \RePart(s)=\tfrac12\Big)\Longrightarrow
\Big(\forall s\in\mathcal{B}\cap\mathcal{A}_{\mathrm{strip}},\ \RePart(s)=\tfrac12\Big)
\]
is not theorem-usable, because the local hypotheses may fail to persist away from $\mathcal{R}_{\mathrm{loc}}$.
\end{drafttheorem}

\paragraph{Proof skeleton for \cref{thm:stage6-first-subtarget-admissibility} (outline only; open).}
This is a schematic work plan, not a proof.
To keep contradiction bookkeeping explicit, the outline is split into premise/support/conclusion blocks:
\begin{enumerate}
  \item \textbf{Premise block (contradiction assumption).}
  Fix $s_\ast\in\mathcal{B}_{\mathrm{tr}}\cap\mathcal{A}_{\mathrm{strip}}$ with $\RePart(s_\ast)\neq\tfrac12$ under $\mathcal{H}_{\mathrm{S6}}^{\min}$, together with a transfer object $C_\ast\in\mathfrak{C}_{\mathrm{tr}}$ from a local anchor to $s_\ast$.
  \item \textbf{Support block (open transport bridge).}
  Invoke the admissibility-stability transfer bridge to transport the exact Stage-5 local hypothesis tuple along $C_\ast$ to the endpoint $s_\ast$ with no hypothesis drift.
  \item \textbf{Conclusion block (local uniqueness at endpoint).}
  Apply the transported Stage-5 uniqueness clause at $s_\ast$.
  \item \textbf{Contradiction extraction.}
  Compare the endpoint uniqueness consequence with $\RePart(s_\ast)\neq\tfrac12$ to produce explicit incompatibility.
  \item \textbf{First-subtarget exclusion conclusion.}
  Deduce
  \[
  \mathcal{B}_{\mathrm{tr}}\cap\{s\in\mathcal{A}_{\mathrm{strip}}:\RePart(s)\neq\tfrac12\}=\varnothing,
  \]
  and record remaining Stage~6 burdens (no-new-off-line-branch and no-alternative-locus) as still open.
\end{enumerate}
The transport and symmetry steps above are where AC1--AC6 and OP7--OP8 support is expected to enter.
The no-new-off-line-branch and no-alternative-locus burdens remain subsequent open targets and are not discharged here.


\subsection*{Audit focus: primary likely failure point in the first contradiction-style Stage~6 target}
To sharpen theorem-status discipline, the manuscript records one \emph{primary likely failure point} in
\cref{thm:stage6-first-subtarget-admissibility}.
This is an audit-priority assessment, not a fatality claim.

\paragraph{Contradiction theorem target (for reference).}
The target theorem is: under one synchronized package $\mathcal{H}_{\mathrm{S6}}^{\min}$, any assumed transfer-reachable off-line balanced point
\[
s_\ast\in\mathcal{B}_{\mathrm{tr}}\cap\mathcal{A}_{\mathrm{strip}},\qquad \RePart(s_\ast)\neq\tfrac12,
\]
should contradict transported Stage-5 uniqueness, yielding
\[
\mathcal{B}_{\mathrm{tr}}\cap\{s\in\mathcal{A}_{\mathrm{strip}}:\RePart(s)\neq\tfrac12\}=\varnothing.
\]
This remains a draft theorem target only.

\paragraph{Primary likely failure point (current highest-risk step).}
The highest-risk step is the \emph{no-drift transport bridge} in item~(4):
passing from local Stage-5 hypotheses on $\mathcal{R}_{\mathrm{loc}}$ to endpoint-valid hypotheses at $s_\ast$ along
$C_\ast\in\mathfrak{C}_{\mathrm{tr}}$ without implicit strengthening, weakening, or type changes in admissibility and regularity clauses.
In current notation, this is precisely the local-to-global synchronization burden across
$\mathcal{R}_{\mathrm{loc}}\subseteq\mathcal{A}_{\mathrm{strip}}$ under $\mathcal{H}_{\mathrm{S6}}^{\min}$.

\paragraph{Why this is the present top audit risk.}
If this transport step is not theorem-level, the contradiction route can become circular or under-typed:
local uniqueness is invoked at $s_\ast$ without proof that the same hypothesis tuple still holds there.
Then the contradiction conclusion is not logically available, even when $s_\ast\in\mathcal{B}$ is assumed.

\paragraph{What would neutralize this risk (required additional result type).}
A theorem-level \emph{transport invariance lemma} is required as a dedicated bridge:
for every transfer path/class element $C\in\mathfrak{C}_{\mathrm{tr}}$ from a local anchor to an endpoint in $\mathcal{A}_{\mathrm{strip}}$, the exact Stage-5 hypothesis tuple is preserved with explicit quantitative control and no predicate drift.
In the current dependency map this means proving the B4a transport bridge with explicit OP7--OP8 and AC1--AC6 usage, under one fixed synchronized package.
Until that bridge is proved, the first contradiction-style Stage~6 theorem remains open.

\subsection*{Best candidate neutralizing result for the current Stage~6 highest-risk step}
To make the next proof attempt executable, the manuscript now names one \emph{single best candidate repair target} for the no-drift transport failure point.
This is a theorem target only.
It is not proved in this manuscript version.

\begin{drafttheorem}[Candidate neutralizing theorem target (Stage~6 transport-uniformity contradiction enabler)]
\label{thm:stage6-neutralizing-transport-uniformity}
\placeholder{Draft theorem target under construction; proof not yet provided.}
Let
\[
\mathcal{A}_{\mathrm{strip}}:=\{s\in\mathcal{A}:0<\RePart(s)<1\},\qquad
\mathcal{B}:=\{s\in\mathcal{A}_{\mathrm{strip}}:\Phi_H(s)=0\},\qquad
\mathcal{R}_{\mathrm{loc}}\subseteq\mathcal{A}_{\mathrm{strip}}.
\]
Work under the same synchronized package $\mathcal{H}_{\mathrm{S6}}^{\min}$ used by
\cref{thm:stage6-first-subtarget-admissibility}, and let
$\mathfrak{C}_{\mathrm{tr}}$ denote the transfer class.
The candidate neutralizing result is the following theorem target.
\begin{enumerate}
  \item \textbf{Hypothesis package required by this target.}
  Use $\mathcal{H}_{\mathrm{S6}}^{\min}$ together with an explicit transport-uniformity clause
  \[
  \mathcal{T}_{\mathrm{nd}}
  \]
  that states (i) endpoint-admissibility persistence, (ii) no-loss regularity persistence, (iii) no-loss symmetry compatibility under reflection/conjugation transport, and (iv) quantitative continuation bounds sufficient to prevent predicate drift along every $C\in\mathfrak{C}_{\mathrm{tr}}$.
  This clause is formulation-level and does not assume a finalized operator realization beyond the OP/AC interface already declared.

  \item \textbf{Exact conclusion needed to neutralize the failure point.}
  For every transfer-reachable endpoint $s\in\mathcal{A}_{\mathrm{strip}}$, if
  $s\in\mathcal{B}_{\mathrm{tr}}$, then the full Stage-5 local hypothesis tuple holds at $s$ in the same theorem-usable form as at local anchors in $\mathcal{R}_{\mathrm{loc}}$.
  Equivalently: there is no hypothesis drift between local and endpoint predicates along transfer paths.

  \item \textbf{How this plugs into the current contradiction route.}
  Under item~(2), any assumed off-line endpoint
  \[
  s_\ast\in\mathcal{B}_{\mathrm{tr}},\qquad \RePart(s_\ast)\neq\tfrac12,
  \]
  is eligible for direct use of the transported Stage-5 uniqueness clause.
  Hence the contradiction step in \cref{thm:stage6-first-subtarget-admissibility} becomes theorem-typed rather than heuristic, and the first-subtarget exclusion conclusion becomes derivable in principle under the same package.

  \item \textbf{What remains open even if this target is proved.}
  This target would neutralize only the current highest-risk failure point.
  It would not by itself prove: (i) no-new-off-line-branch exclusion outside transfer-reachable classes, (ii) the no-alternative-locus theorem target on all of $\mathcal{B}$, or (iii) the full master Stage~6 exclusion theorem on $\mathcal{A}_{\mathrm{strip}}$.
\end{enumerate}
\paragraph{Status label.}
Open theorem target (candidate repair only).
No proof is supplied here.
\end{drafttheorem}

\subsection*{First concrete lemma target toward the neutralizing theorem (single next move; open)}
To move from architecture-level planning to an executable first proof step, the manuscript fixes one concrete lemma target as the immediate predecessor to \cref{thm:stage6-neutralizing-transport-uniformity}.
This is a statement target only.
No proof is claimed.

\begin{drafttheorem}[First concrete Stage~6 lemma target: uniform no-drift transport of the Stage-5 tuple]
\label{lem:stage6-first-concrete-no-drift}
\placeholder{Draft lemma target under construction; proof not yet provided.}
Let
\[
\mathcal{A}_{\mathrm{strip}}:=\{s\in\mathcal{A}:0<\RePart(s)<1\},\qquad
\mathcal{R}_{\mathrm{loc}}\subseteq\mathcal{A}_{\mathrm{strip}},
\]
and work under one synchronized package $\mathcal{H}_{\mathrm{S6}}^{\min}$ with transfer class $\mathfrak{C}_{\mathrm{tr}}$.
Write $\Theta_{\mathrm{S5}}$ for the full Stage-5 hypothesis tuple used in local uniqueness.
The first concrete lemma target is:
\begin{quote}
For every transfer object $C\in\mathfrak{C}_{\mathrm{tr}}$ connecting a local anchor in $\mathcal{R}_{\mathrm{loc}}$ to an endpoint in $\mathcal{A}_{\mathrm{strip}}$, the tuple $\Theta_{\mathrm{S5}}$ persists at every transfer position and at the endpoint with one uniform control profile valid across the transfer class used by the contradiction step.
\end{quote}
Equivalently, this lemma target excludes hypothesis drift (admissibility, regularity, or symmetry loss) along the transfer class relevant to the first contradiction attempt.

\paragraph{Feeds into relation.}
This lemma is strictly downstream of the first contradiction target \cref{thm:stage6-first-subtarget-admissibility} and its highest-risk no-drift step, and strictly upstream of the neutralizing theorem target \cref{thm:stage6-neutralizing-transport-uniformity}.
It does not replace that neutralizing theorem; it is the first concrete proving move toward it.

\paragraph{Status label.}
Open lemma target (not proved).
\end{drafttheorem}

\subsection*{Technical character classification of the current neutralizing result (audit judgment)}
This subsection classifies \cref{thm:stage6-neutralizing-transport-uniformity} for proof-planning clarity.
The classification is an audit judgment about current dependency structure.
It is not a proved meta-theorem.

\paragraph{Classification.}
\textbf{Current reading: genuinely mixed, with primarily analytic dominant burden and operator-theoretic supporting burden.}

\paragraph{Neutralizing result itself (what is being classified).}
The neutralizing target is the no-drift transport-uniformity bridge:
transfer-reachable endpoints in $\mathcal{B}_{\mathrm{tr}}$ must inherit the exact Stage-5 hypothesis tuple from $\mathcal{R}_{\mathrm{loc}}$ under one synchronized package $\mathcal{H}_{\mathrm{S6}}^{\min}$.
This is a theorem target only.

\paragraph{Why this is genuinely mixed.}
The target is mixed because both sides are structurally necessary in the current formulation:
\begin{enumerate}
  \item \textbf{Analytic-control side:} continuation/compactness/uniformity and interchange legitimacy are needed to carry hypotheses along $\mathfrak{C}_{\mathrm{tr}}$ without drift across strip regimes.
  \item \textbf{Operator side:} admissibility and symmetry transport must remain typed and stable under the operator transformations actually used by the transfer class.
\end{enumerate}
Without either side, the contradiction route is not theorem-typed.

\paragraph{Dominant burden versus supporting burden in the present first proving attempt.}
For the current first proving target (\cref{thm:stage6-first-subtarget-admissibility}), the dominant burden appears on the analytic side:
\begin{enumerate}
  \item the highest-risk step is no-drift transport through boundary-near, non-perturbative, and large-parameter strip sectors;
  \item this risk is carried mainly by AC-style requirements (uniform control and continuation validity), not by selecting additional operator structure;
  \item OP-side requirements are still necessary, but mainly to keep admissibility/symmetry transport well-typed once analytic transport control is available.
\end{enumerate}
Hence the manuscript treats the current neutralizing theorem target as \emph{mixed with analytic dominance}.

\paragraph{Downstream consequence if eventually proved (still conditional).}
If the neutralizing target were proved under synchronized hypotheses, the contradiction step in
\cref{thm:stage6-first-subtarget-admissibility} would become theorem-usable for $\mathcal{B}_{\mathrm{tr}}$.
This would remove the currently identified no-drift typing failure point.
It would not by itself prove no-alternative-locus on all of $\mathcal{B}$ or the master Stage~6 exclusion endpoint.

\paragraph{Three-way separation (local result, transfer bridge, global conclusion).}
To avoid conflation of proof burdens:
\begin{enumerate}
  \item \textbf{Local Target~B control (Stage~5):} uniqueness on $\mathcal{R}_{\mathrm{loc}}$ only.
  \item \textbf{Transfer bridge (Stage~6 target):} \cref{thm:transfer-target-B}, carrying local control to $\mathcal{A}_{\mathrm{strip}}$.
  \item \textbf{Global exclusion conclusion:} no off-line balanced points anywhere in $\mathcal{A}_{\mathrm{strip}}$.
\end{enumerate}
The manuscript records item (2) as an open theorem target, not as a proved corollary of item (1).

\paragraph{What must be transferred.}
For closure, $\mathcal{H}_{\mathrm{tr}}$ must carry all of the following from local to global:
\begin{enumerate}
  \item local uniqueness on/near $\RePart(s)=\tfrac12$;
  \item local exclusion of off-line balanced points in $\mathcal{R}_{\mathrm{loc}}$;
  \item continuation/compactness/uniformity control needed to extend estimates through the full strip class;
  \item prevention of hidden off-line components of $\mathcal{B}$ outside $\mathcal{R}_{\mathrm{loc}}$.
\end{enumerate}

\paragraph{Likely hypothesis classes (model not fixed).}
Without selecting a finalized operator realization, a viable transfer target will likely need:
\begin{enumerate}
  \item admissibility stability across local and global regimes;
  \item compatibility of local estimates with the full admissible strip class;
  \item continuation/compactness/uniformity hypotheses preventing loss of control outside $\mathcal{R}_{\mathrm{loc}}$;
  \item no-loss symmetry compatibility under reflection/conjugation transport;
  \item explicit exclusion of new alternative-locus branches appearing only outside local control.
\end{enumerate}
These remain open assumptions/targets in this manuscript version.

\subsection*{No-alternative-locus principle for the balanced set \texorpdfstring{$\mathcal{B}$}{B} (theorem target)}
This subsection isolates a distinct Stage~6 theorem target.
It does not assert a proved theorem.
In the current route, this is a sub-burden for \cref{thm:stage6-master-exclusion-target}, not a separate endpoint.

\paragraph{Balanced-set notation and target form.}
Let
\[
\mathcal{B}:=\{s\in\mathcal{A}_{\mathrm{strip}}:\Phi_H(s)=0\},\qquad
\mathcal{A}_{\mathrm{strip}}:=\{s\in\mathcal{A}:0<\RePart(s)<1\}.
\]
The no-alternative-locus target is:
\begin{quote}
Under one synchronized hypothesis package $\mathcal{H}_{\mathrm{NAL}}$, every connected component of $\mathcal{B}$ is contained in $\RePart(s)=\tfrac12$.
\end{quote}
Equivalent set form:
\[
\mathcal{B}\subseteq \{s\in\mathcal{A}_{\mathrm{strip}}:\RePart(s)=\tfrac12\}.
\]

\paragraph{What this target must rule out explicitly.}
For theorem-level closure, $\mathcal{H}_{\mathrm{NAL}}$ must exclude each of the following possibilities:
\begin{enumerate}
  \item an alternative vertical balance line $\RePart(s)=\sigma_0\neq\tfrac12$;
  \item a curve/submanifold of off-line balanced points in $\mathcal{A}_{\mathrm{strip}}$;
  \item disconnected off-line components of $\mathcal{B}$;
  \item regime-specific off-line loci that appear only outside the local uniqueness regime $\mathcal{R}_{\mathrm{loc}}$.
\end{enumerate}

\paragraph{Hypothesis classes required by the target (model not yet fixed).}
Without choosing a finalized operator realization, the theorem target requires explicit hypotheses of the following kinds:
\begin{enumerate}
  \item admissibility synchronization across Target~A, local Target~B, and Stage~6 transfer;
  \item symmetry compatibility under $s\mapsto 1-s$ and $s\mapsto\bar s$ on the same admissible class;
  \item one or more global rigidity/coercivity/positivity/transfer ingredients;
  \item analytic-control assumptions that prevent hidden off-line branches from boundary or large-parameter regimes.
\end{enumerate}
This manuscript version records these as open obligations, not established facts.

\paragraph{Relation to the contradiction route.}
The contradiction route (assume an off-line balanced $s_\ast$ and derive incompatibility) is a \emph{method} candidate.
The no-alternative-locus principle is the \emph{theorem target} that method is meant to establish.
These are related but not identical statements:
\begin{enumerate}
  \item \textbf{Local uniqueness (Stage 5):} excludes off-line balance only in $\mathcal{R}_{\mathrm{loc}}$.
  \item \textbf{No-alternative-locus target (Stage 6):} excludes every off-line component in the full admissible strip.
  \item \textbf{Contradiction route template:} provides a candidate proof path from an assumed off-line point to failure of a synchronized Stage~6 ingredient.
\end{enumerate}
Keeping these separate avoids conflating a local statement, a global theorem target, and a prospective proof mechanism.

\subsection*{Why symmetry alone is insufficient}
Classical symmetries give transport rules ($s\mapsto1-s$, $s\mapsto\bar s$).
They do not by themselves imply that the only balance-supporting locus is $\RePart(s)=\tfrac12$.
An argument can preserve symmetry and still allow paired off-line candidates.
Hence the framework requires a separate exclusion mechanism beyond symmetry compatibility.

\subsection*{Candidate exclusion mechanism template (audit-level theorem scaffold)}
This subsection records a \emph{template} for the missing Stage~6 ingredient.
It is not a proof claim.
Its purpose is to specify what theorem shape would be required to rule out admissible off-line balanced points.

\paragraph{Template input package $\mathcal{E}$.}
A candidate exclusion theorem would need, at minimum, a synchronized hypothesis package containing:
\begin{enumerate}
  \item a well-posed balance functional $\Phi_H$ on the full admissible strip class $\mathcal{A}_{\mathrm{strip}}$;
  \item a local Target~B statement on a declared regime $\mathcal{R}_{\mathrm{loc}}\subseteq\mathcal{A}_{\mathrm{strip}}$;
  \item one or more \emph{global control ingredients} (model-dependent), such as coercivity, positivity, monotonicity, rigidity, or another explicit structural inequality;
  \item a transfer principle extending the relevant control from $\mathcal{R}_{\mathrm{loc}}$ to the full strip regime required by the reduction;
  \item symmetry-compatibility assumptions sufficient to move between reflected/conjugate candidates without changing theorem hypotheses.
\end{enumerate}

\paragraph{Template theorem target (not yet proved).}
A mechanism of the required type would support a theorem with the following form:
\begin{quote}
Under $\mathcal{E}$, no $s\in\mathcal{A}_{\mathrm{strip}}$ with $0<\RePart(s)<1$ and $\RePart(s)\neq\tfrac12$ can satisfy $\Phi_H(s)=0$.
\end{quote}
Equivalent contradiction form: assuming an admissible off-line balanced point exists forces violation of at least one ingredient in $\mathcal{E}$ (for example the coercive/positive/rigidity control or the transfer hypothesis).

\paragraph{Structural mechanism classes (abstract, model-dependent).}
Without fixing a finalized operator model, the manuscript currently treats the following as plausible \emph{classes} of exclusion mechanisms:
\begin{enumerate}
  \item \textbf{Coercive gap mechanism:} prove a quantitative lower bound for an off-line defect functional that is strictly positive away from $\RePart(s)=\tfrac12$ and incompatible with balance.
  \item \textbf{Positivity/monotonicity mechanism:} identify a strip-parameterized quantity whose sign or monotone drift prevents return to exact balance off the axis.
  \item \textbf{Rigidity mechanism:} show that equality in a key estimate can occur only on the critical line, so off-line balance violates the equality conditions.
  \item \textbf{Reflection-incompatibility mechanism:} combine transport symmetries with an admissibility constraint so that an off-line balanced candidate and its reflected partner cannot simultaneously satisfy the same admissible balance law.
  \item \textbf{Local-to-global closure mechanism:} prove that any off-line balanced candidate would have to enter a locally excluded regime, yielding contradiction with Target~B localization.
\end{enumerate}
These are mechanism templates only.
Any accepted version must be converted into explicit lemmas with hypotheses and dependency tracing.

\subsection*{Preferred Stage~6 theorem path (current manuscript choice; conditional)}
\label{subsec:preferred-stage6-route}
The manuscript now designates one \emph{preferred theorem path} for Stage~6:
\begin{quote}
\textbf{Primary route: local-to-global closure for $\mathcal{B}$ culminating in a no-alternative-locus theorem target.}
\end{quote}
Concretely, the intended logical route is
\[
\text{Stage-5 local uniqueness on }\mathcal{R}_{\mathrm{loc}}
\Longrightarrow
\text{transfer/closure on }\mathcal{A}_{\mathrm{strip}}
\Longrightarrow
\text{no off-line component of }\mathcal{B}.
\]
This is a planning decision for proof development under audit.
It is \emph{not} a claim that the route has been proved.
The route is organized to prove the single master target \cref{thm:stage6-master-exclusion-target} under $\mathcal{H}_{\mathrm{S6}}^{\min}$.

\paragraph{Why this is the current preferred route.}
This route is currently the most coherent fit with the existing architecture because:
\begin{enumerate}
  \item Stage~5 already isolates a local uniqueness burden, so a transfer theorem is the direct missing bridge to full-strip exclusion;
  \item the no-alternative-locus target is the clean global statement needed by the Stage~6 conclusion;
  \item the same route aligns with the existing OP/AC burden split (operator-side admissibility stability plus analytic continuation/compactness control);
  \item it keeps theorem targets aligned with the current dependency stack in \texttt{proof-architecture.tex} and \texttt{lemmas.tex}.
\end{enumerate}

\paragraph{Role of the other mechanism classes relative to the preferred route.}
The manuscript keeps all mechanism classes visible, but assigns them different roles:
\begin{enumerate}
  \item \textbf{Primary sub-mechanisms (inside the preferred route):}
  local-to-global closure, no-hidden-branch control, and no-alternative-locus closure for $\mathcal{B}$.
  \item \textbf{Supporting ingredients (to make transfer/no-alternative-locus provable):}
  coercive gap estimates, positivity/monotonic drift controls, and rigidity/equality-case controls.
  In the current strategy, these are not independent Stage~6 endpoints; they are candidate tools for proving the transfer and closure bridges.
  \item \textbf{Secondary/fallback routes:}
  reflection-incompatibility and direct contradiction-under-assumed-off-line-balance arguments.
  These remain viable alternatives if the primary closure route stalls, but are not the leading theorem path in this revision.
\end{enumerate}

\paragraph{Unresolved dependencies for the preferred route.}
Before the preferred route can become a proof, the manuscript still requires theorem-level closure of:
\begin{enumerate}
  \item Stage-5 local uniqueness under explicit hypotheses;
  \item a synchronized transfer package (admissibility stability, continuation/compactness uniformity, and symmetry-compatible transport);
  \item no-hidden-off-line-component control for $\mathcal{B}$ outside $\mathcal{R}_{\mathrm{loc}}$;
  \item at least one proved global-control ingredient (coercive/positivity/rigidity class) strong enough to close no-alternative-locus;
  \item hypothesis synchronization with Target~A correspondence assumptions.
\end{enumerate}
All five items remain open in the current manuscript version.

\subsection*{Candidate contradiction route under an assumed off-line balanced point (template only)}
This subsection makes the Stage~6 contradiction burden explicit in assumption-conclusion form.
It does not claim that a contradiction has been proved.
It records the cleanest theorem shape currently targeted for audit.

\paragraph{Assumed off-line balanced point package $\mathcal{O}_{\mathrm{off}}$.}
Assume there exists
\[
 s_\ast\in \mathcal{A}_{\mathrm{strip}},\qquad 0<\RePart(s_\ast)<1,\qquad \RePart(s_\ast)\neq\tfrac12,
\]
with $\Phi_H(s_\ast)=0$.
For this assumption to be meaningful inside the framework, $s_\ast$ must satisfy all of the following at once:
\begin{enumerate}
  \item \textbf{Admissibility:} $s_\ast$ lies in the same admissible class used in Targets~A/B and Stage~6 transfer.
  \item \textbf{Balance validity:} $\Phi_H(s_\ast)$ is well defined under the declared domain/regularity hypotheses, and exact balance means $\Phi_H(s_\ast)=0$ in that theorem-level sense.
  \item \textbf{Reflection/conjugation compatibility:} the transported points $1-s_\ast$ and $\overline{s_\ast}$ (and thus the quartet closure when required) remain inside the same admissible/regularity package.
  \item \textbf{Regularity regime compatibility:} $s_\ast$ lies in the strip regime where all global-control and transfer assumptions are stated (including boundary-near and large-parameter side conditions, if invoked).
\end{enumerate}

\paragraph{Contradiction route target $\mathcal{C}_{\mathrm{route}}$ (not proved).}
Under one synchronized Stage~6 hypothesis package $\mathcal{E}_{\mathrm{glob}}$, the manuscript aims to show:
\begin{quote}
Assumption $\mathcal{O}_{\mathrm{off}}$ forces failure of at least one theorem-level ingredient in $\mathcal{E}_{\mathrm{glob}}$; therefore no admissible off-line balanced point exists.
\end{quote}
The contradiction endpoint should be formalized as one of the following mechanism classes (or another explicitly stated equivalent):
\begin{enumerate}
  \item violation of a coercive/positive quantity required to stay nonnegative or strictly positive away from $\RePart(s)=\tfrac12$;
  \item incompatibility with a uniqueness/rigidity equality case used by Target~B localization;
  \item contradiction with symmetry-compatible transfer between $s_\ast$, $1-s_\ast$, and conjugates;
  \item impossibility of extending local balance consistently into the full-strip regime;
  \item conflict with a no-alternative-locus principle for exact balance under the same assumptions.
\end{enumerate}

\paragraph{Three-layer audit split for the contradiction route.}
To avoid proof-status ambiguity, Stage~6 is recorded in three layers:
\begin{enumerate}
  \item \textbf{Assumption layer:} existence of an admissible off-line balanced point satisfying $\mathcal{O}_{\mathrm{off}}$.
  \item \textbf{Support-lemma layer:} intermediate contradiction-support lemmas (global extension, quartet transfer, coercive/rigidity/positivity bridge, or equivalent) under one synchronized package.
  \item \textbf{Conclusion layer:} formal contradiction and full-strip no-off-line-balance theorem target.
\end{enumerate}
This separation is aligned with Target~B local uniqueness versus Stage~6 global exclusion.

\paragraph{Open proof obligations tied to this template.}
To promote this template to theorem-level closure, the manuscript still needs:
\begin{enumerate}
  \item a finalized statement of the chosen global control ingredient(s);
  \item proof that those ingredients are valid on the declared admissible strip class;
  \item a proved transfer theorem from local control to global strip control;
  \item a contradiction theorem excluding every admissible off-line balanced point under one common hypothesis package.
\end{enumerate}
These obligations are part of the open bridges listed in \texttt{lemmas.tex} and \texttt{notes/known-gaps.md}.

\subsection*{Reduction proof skeleton (conditional)}
The deduction itself is short once the above inputs are available.
Let $\rho$ be a nontrivial zero.
By Target A, $\rho$ maps to a balanced admissible configuration.
By Target B, that balanced configuration must lie on $\RePart(s)=\tfrac12$.
Hence $\RePart(\rho)=\tfrac12$.
The global off-line exclusion package ensures that no admissible off-line cases survive outside the local regime used to prove Target B, so the conclusion applies across the entire critical strip addressed by $\mathcal{A}$.

\subsection*{Where the argument is formally straightforward}
\begin{itemize}
  \item The final implication from ``zero is balanced'' plus ``balanced implies critical line'' to RH-in-strip is a direct composition of statements.
  \item No deep analytic estimate enters at this final step once hypotheses are synchronized and side conditions are already checked.
\end{itemize}

\subsection*{Where the unresolved burden lies}
The mathematical pressure is upstream, not in the final deduction.
The unresolved burden is to prove, under explicit assumptions, the six core open bridges that feed the reduction:
\begin{enumerate}
  \item \textbf{Exact spectral object burden:} finalize the $H$-layer with explicit domain/action/symmetry data and proof-level well-posedness.
  \item \textbf{Zero--balance correspondence burden (Target A):} establish a rigorous correspondence map with precise domain/codomain control, including both directions and exclusion of spurious balanced states.
  \item \textbf{Uniqueness-of-axis burden (Target B):} prove a theorem-level localization statement forcing every admissible balanced point onto $\RePart(s)=\tfrac12$.
  \item \textbf{Off-critical-line exclusion burden:} upgrade local or regime-restricted arguments to a full-strip exclusion theorem compatible with the assumptions used in Targets A and B.
  \item \textbf{Operator-theoretic burden:} prove each operator property actually used in Targets A/B and exclusion (no hidden assumptions).
  \item \textbf{Analytic-control burden:} justify every growth/convergence/interchange step needed to pass from local constructions to strip-wide statements.
\end{enumerate}
Until these bridges are proved, the reduction remains conditional.

\subsection*{Insufficient argument patterns (explicitly excluded)}
The manuscript does not treat the following as adequate for Target~B or global exclusion:
\begin{enumerate}
  \item \textbf{Pure symmetry arguments} that establish only mirrored pairing of candidate points.
  \item \textbf{Local-only coercivity} without a theorem transferring estimates to the full admissible strip.
  \item \textbf{Regime-fragmented proofs} whose hypotheses differ across subregions without compatibility/patching lemmas.
  \item \textbf{Numerical-only exclusion} not converted into theorem-level analytic statements.
\end{enumerate}

\subsection*{Assumption-compatibility requirements}
For the reduction to be valid as stated, the assumptions used in Target A, Target B, and global off-line exclusion must be mutually compatible.
In particular, the manuscript must avoid: (i) proving Target A on one admissible class and Target B on a narrower incompatible class without a transfer theorem, and (ii) invoking a global exclusion principle whose hypotheses are not inherited by the correspondence setup.

\begin{remark}[Audit-facing interpretation]
This section does \emph{not} claim that RH is proved.
It states that the framework yields RH \emph{if} Targets A and B and the global off-line exclusion package are established under a common explicit hypothesis set.
The hard work is proving those prior bridges.
\end{remark}

\begin{remark}[Common failure modes in RH-type reductions]
Two recurring failure modes are especially relevant here.
First, a correspondence theorem may hold only with hidden regularity assumptions, leaving uncovered zero candidates.
Second, a localization argument may be valid only in a perturbative or local regime and fail to imply global off-line exclusion.
The present framework therefore keeps Target A, Target B, and global exclusion as separate proof obligations.
\end{remark}

\openbridge{Current manuscript status: the conditional deduction is structurally clear, but the six core bridges (exact spectral object, zero--balance correspondence, uniqueness of the balance axis, off-critical-line exclusion, operator-theoretic closure, analytic-control closure) remain open proof obligations requiring full theorem-level proofs under synchronized assumptions.}
