This discussion section is interpretive rather than part of the formal proof flow. It is included to clarify scope, dependencies, and comparison points for mathematical audit.

\paragraph{What this framework attempts to contribute.}
The manuscript proposes a proof framework in which a spectral-coherence construction is used to organize the Riemann Hypothesis (RH) into explicit operator-theoretic and analytic subclaims. The intended contribution is not a stand-alone classical spectral theorem, but a structured reduction: if the listed bridges are proved under the stated assumptions, then the RH conclusion would follow within the manuscript architecture. In this sense, the current value of the framework is traceability. It makes the logical dependency graph visible, distinguishes proved components from provisional ones, and isolates the points where new arguments are still required.

\paragraph{What remains unresolved.}
Several steps remain open and are not presented as established results. In particular, the manuscript still requires formal justification of the bridge statements connecting the coherence functional, the operator model, and the zero-location conclusion. These bridges currently function as targeted obligations, not completed proofs. Numerical checks and consistency tests can support plausibility and help detect contradictions, but they do not close these obligations. The manuscript should therefore be read as an argument that attempts to show how RH could follow from a specific spectral-coherence mechanism, conditional on unresolved proof steps that are explicitly identified.
The current revision makes the Stage~6 burden more explicit by separating: (i) local critical-line uniqueness, (ii) a global no-alternative-locus theorem target for the balanced set $\mathcal{B}$, and (iii) a candidate contradiction route under an assumed admissible off-line balanced point. This is a template for what must be proved, not evidence that the contradiction has already been derived.
Within that template, the manuscript now prioritizes one route: local-to-global transfer for $\mathcal{B}$ followed by no-alternative-locus closure, then full-strip exclusion. The route is now formulated under a named minimum synchronized package $\mathcal{H}_{\mathrm{S6}}^{\min}$ to make assumptions explicit for audit. This naming is a statement-format choice, not a sufficiency theorem. Coercive/positivity/rigidity ingredients are treated as supporting tools for this route. Reflection-incompatibility and direct contradiction-only closures are retained as secondary fallback paths. This prioritization is a proof-strategy choice under audit, not a theorem claim.
The current revision also states one master Stage~6 exclusion theorem target as the single endpoint of that preferred route: under $\mathcal{H}_{\mathrm{S6}}^{\min}$, local uniqueness on $\mathcal{R}_{\mathrm{loc}}$ should transfer to full-strip exclusion of off-line balanced points in $\mathcal{A}_{\mathrm{strip}}$, equivalently $\mathcal{B}\subseteq\{s:\RePart(s)=\tfrac12\}$. For audit readability, the same endpoint is listed in pointwise, set-theoretic, component/locus, and contradiction-style forms under that same package. This is a formulation-level alignment device, not a proof that these forms are established as facts in the current manuscript version.


\subsection*{Current first proving target inside the preferred Stage~6 route}
Within the preferred route
\[
\text{local uniqueness on }\mathcal{R}_{\mathrm{loc}}
\Rightarrow
\text{transfer on }\mathcal{A}_{\mathrm{strip}}
\Rightarrow
\text{no-alternative-locus}
\Rightarrow
\text{full-strip exclusion},
\]
the manuscript now identifies one first subtheorem to try proving:
\begin{quote}
\textbf{Admissibility-stability transfer lemma target (B4 entry lemma):}
local Stage-5 hypotheses must remain valid along the continuation classes used to pass from $\mathcal{R}_{\mathrm{loc}}$ to $\mathcal{A}_{\mathrm{strip}}$.
\end{quote}
Status label: \emph{open theorem target} (not proved).

This is chosen as the best entry point for the current architecture because it is the earliest non-optional dependency in the preferred Stage~6 chain:
\begin{enumerate}
  \item the transfer theorem target cannot even be stated in a theorem-usable way unless admissibility is synchronized from local to strip-wide regimes;
  \item no-hidden-off-line-component and no-alternative-locus targets both presuppose this synchronization;
  \item this entry point does not require selecting a finalized operator realization beyond the existing OP/AC interface assumptions already recorded as open.
\end{enumerate}
Accordingly, the proving order is explicitly: master Stage~6 endpoint (open) $\rightarrow$ first proving target (admissibility-stability transfer, open) $\rightarrow$ later subtargets (uniform continuation/compactness, no-new-off-line-branch, no-alternative-locus, full-strip exclusion).
This ordering is a strategy decision for audit and work planning.
It is not evidence that any Stage~6 bridge has been discharged.

\paragraph{Relation to nearby spectral programs.}
The framework is adjacent to classical spectral programs in the broad sense that it seeks a spectral encoding of information about zeta zeros. However, it is not identical to standard formulations that center a single self-adjoint operator with a fully established spectral correspondence. Here, the emphasis is on a coherence-based architecture and on reduction through intermediate analytic objects. This placement is best interpreted as \emph{neighboring} the classical spectral agenda rather than claiming equivalence to any established program. Similar motivation does not imply interchangeability of technical hypotheses or proof obligations.

\paragraph{Why an audit-first posture is necessary.}
For a claim of this scale, presentation quality is a mathematical issue, not merely editorial preference. An audit-first posture enforces explicit assumptions, conservative claim language, and visible separation between theorem-level content and heuristic interpretation. This reduces the risk of overstating partial results and allows reviewers to evaluate the framework component-by-component. It also improves falsifiability: if a bridge fails, the failure can be localized without ambiguity about what had actually been proved.

\paragraph{Interpretation versus proof.}
Interpretive statements in this section should not be read as additional evidence for the formal claims. Their role is to guide expert reading of the manuscript's scope and status. Formal validity is determined only by the definitions, lemmas, propositions, and theorems together with their hypotheses and dependencies.

\paragraph{Forward path.}
For this framework to mature into a proof, each open bridge must be replaced by a complete argument with explicit hypotheses, the operator/coherence correspondence must be established in full technical detail, and all conditional steps must be eliminated or discharged by cited theorems. At that point, independent verification would need to confirm that the final chain of implications is gap-free.
