This section records the present limits of the argument and identifies the exact burden of proof that remains.
It is written for mathematical audit: each unresolved bridge is stated explicitly so that reviewers can test the framework at its most vulnerable points.

\subsection*{Scope and evidentiary standard}
The manuscript proposes a proof framework.
Its intuitive geometric language is intended to guide construction and suggest mechanisms, but it does not by itself constitute proof.
Only statements supported by complete definitions, hypotheses, and logically valid derivations should be treated as formal results.

\subsection*{Primary open bridges}
\begin{enumerate}
  \item \textbf{Rigorous operator construction.}
  The operator/spectral construction must be specified on a precise functional-analytic domain, with well-defined action, closure properties, and spectral meaning.
  At present, this construction is programmatic rather than complete.
  Any downstream claim that depends on the spectrum is therefore conditional on this step.

  \item \textbf{Proof of the zero--balance equivalence.}
  Any claimed equivalence between the proposed balance criteria and nontrivial zeros of $\zeta(s)$ must be proved as a theorem in both directions.
  This equivalence cannot be assumed from analogy, numerics, or partial correspondences.
  Until a full equivalence proof is written, the balance criteria should be treated as candidate reformulations.

  \item \textbf{Rigorous uniqueness of the critical line.}
  The argument requires a proof that the relevant mechanism selects $\Re(s)=\tfrac12$ uniquely, not merely that it is compatible with that line.
  Exclusion of off-line alternatives must be established by explicit estimates or structural theorems under stated hypotheses.
  Without such a proof, uniqueness of the critical line remains open within this framework.
\end{enumerate}

\subsection*{Operator-theoretic failure mode (explicit Stage-2/Stage-6 risk)}
The operator burden is an open bridge with concrete failure modes, not a generic warning.
The balance framework and exclusion route fail as theorem-level arguments if any of the following operator-side items is missing under the chosen model:
\begin{enumerate}
  \item no proof-level ambient-space/domain specification for $H$ matching later lemmas;
  \item no proved closure/closability or graph control where later spectral steps require it;
  \item no proved domain invariance under reflection/conjugation (or other declared symmetry transport);
  \item no explicit intertwining/covariance identity linking operator symmetry to the balance law $\Phi_H$;
  \item use of spectral constructions without a proved legitimacy theorem in the declared operator setting;
  \item failure to prove that operator-side transformations preserve admissibility hypotheses used in local-to-global transfer;
  \item mismatch between operator assumptions used in Target~A/Target~B and those used in Stage~6 exclusion.
\end{enumerate}
Accordingly, the manuscript requires an explicit operator-theoretic support package (OP1--OP8 in \texttt{spectral-framework.tex} and \texttt{lemmas.tex}), with each item proved or explicitly imported in one synchronized hypothesis package.
Until this package is discharged, correspondence, uniqueness transfer, and full-strip exclusion remain conditional.

\subsection*{Analytic-control failure mode (explicit Stage-6 risk)}
The analytic-control burden is an open bridge, not a generic caution.
For the local-to-global transfer and full-strip exclusion steps, failure of any one of the following would invalidate the Stage~6 route even if local Target~B were available:
\begin{enumerate}
  \item missing strip-wide growth bounds in boundary-near or large-parameter sectors;
  \item non-uniform convergence in representations used to transport local estimates;
  \item unjustified interchange operations (limit/integral, derivative/integral, summation/integration, contour deformation);
  \item continuation/compactness failure that blocks extension from $\mathcal{R}_{\mathrm{loc}}$ to $\mathcal{A}_{\mathrm{strip}}$;
  \item hidden off-line branch emergence for $\mathcal{B}=\{s\in\mathcal{A}_{\mathrm{strip}}:\Phi_H(s)=0\}$ outside locally controlled regimes;
  \item incompatibility between local estimates and strip-wide admissibility hypotheses.
\end{enumerate}
Accordingly, Stage~6 requires an explicit analytic-control theorem package (AC1--AC6 in \texttt{spectral-framework.tex} and \texttt{lemmas.tex}), with each item either proved or declared as a synchronized assumption. Until that package is discharged, no theorem-level full-strip exclusion claim is available in this manuscript.


\subsection*{Status of the minimum Stage~6 hypothesis package}
The manuscript now names a minimum synchronized package $\mathcal{H}_{\mathrm{S6}}^{\min}$ for the preferred Stage~6 route (local uniqueness $\to$ transfer $\to$ no-alternative-locus $\to$ full-strip exclusion).
This package is a formulation scaffold only.
It specifies the minimum assumptions required to state the target theorem cleanly under one synchronized hypothesis set.
The target theorem in view is the master Stage~6 exclusion statement: under $\mathcal{H}_{\mathrm{S6}}^{\min}$, local uniqueness on $\mathcal{R}_{\mathrm{loc}}$ extends to global strip exclusion of off-line balanced points, equivalently $\mathcal{B}\subseteq\{s\in\mathcal{A}_{\mathrm{strip}}:\RePart(s)=\tfrac12\}$.
For audit clarity, the same endpoint is tracked in pointwise, set-theoretic, component/locus, and contradiction-style formulations under the same synchronized package.
This is recorded as an open theorem target for audit.
It does not establish that those assumptions are jointly sufficient for a proof.
It does not assert that any package item is already proved.
Any later sufficiency claim would require a separate theorem-level argument that discharges every dependency without hypothesis drift.
The manuscript now also names a first Stage~6 subtheorem target and, within it, one single best first technical move: the concrete lemma target of uniform no-drift transport of the Stage-5 hypothesis tuple along $\mathfrak{C}_{\mathrm{tr}}$.
This target is now stated as the draft theorem \cref{thm:stage6-first-subtarget-admissibility} in explicit contradiction-ready form, together with a separate proof-skeleton outline.
Both the theorem and the skeleton are explicitly open and conditional.
The contradiction-ready formatting is intended to make a line-by-line proof attempt executable for audit; it is not evidence of completion.
This is a strategy and dependency-order decision only.
It does not establish that the subtheorem is proved, nor that proving it alone would complete Stage~6.
The associated no-drift defect functional $\Delta_{\mathrm{nd}}$ is also provisional in this manuscript version: it is defined at the OP/AC interface level for audit and proof planning, and may be revised when a finalized operator realization and transfer model are fixed.


\subsection*{Highest-risk point in the current first Stage~6 contradiction attempt}
The manuscript now identifies a single highest-risk step in the current first contradiction-style subtheorem
(\cref{thm:stage6-first-subtarget-admissibility}).
This is not presented as fatal.
It is presented as the current top audit risk.

\paragraph{Contradiction target being attempted.}
Under $\mathcal{H}_{\mathrm{S6}}^{\min}$, the first target attempts to show that no transfer-reachable off-line balanced point survives:
\[
\mathcal{B}_{\mathrm{tr}}\cap\{s\in\mathcal{A}_{\mathrm{strip}}:\RePart(s)\neq\tfrac12\}=\varnothing.
\]

\paragraph{Primary likely failure point.}
The likely failure point is the no-drift transport claim that the exact Stage-5 local hypothesis tuple persists from
$\mathcal{R}_{\mathrm{loc}}$ to endpoint candidates in $\mathcal{A}_{\mathrm{strip}}$ along $\mathfrak{C}_{\mathrm{tr}}$ under unchanged predicates.
If this step is underjustified, the contradiction can call local uniqueness at an endpoint where local hypotheses were never theorem-level re-established.

\paragraph{Neutralization criterion.}
To neutralize this risk, the manuscript needs a theorem-level transport invariance result with explicit dependency control:
for each relevant transfer object, admissibility, regularity, symmetry-compatibility, and well-posedness clauses used by Stage~5 are preserved without hidden hypothesis switching.
In current notation this is the B4a first-concrete bridge (\cref{lem:b4-admissibility-stability-transfer}), with explicit OP7--OP8 and AC1--AC6 support under one synchronized package.
Until this bridge is proved, the first Stage~6 contradiction attempt remains open.

\paragraph{Current best candidate repair target (explicitly open).}
The manuscript now names one best candidate neutralizing result:
\cref{thm:stage6-neutralizing-transport-uniformity} in \texttt{critical-line-argument.tex}.
This target is a theorem-level contradiction-enablement bridge under $\mathcal{H}_{\mathrm{S6}}^{\min}$:
it aims to show that every transfer-reachable endpoint inherits the exact Stage-5 hypothesis tuple with no predicate drift along $\mathfrak{C}_{\mathrm{tr}}$.
Status remains open.
This is a repair target, not a proved fix.
Likewise, the first concrete lemma is a current proving-move designation, not an established result.

\paragraph{Technical-character classification (audit judgment; not a theorem claim).}
Current manuscript reading classifies this neutralizing target as \emph{genuinely mixed}, with \emph{analytic dominant burden} and \emph{operator-theoretic supporting burden}.
This classification is based on the present dependency architecture (AC1--AC6 carrying the no-drift transport control; OP7--OP8 with invoked OP1--OP6 keeping transport assumptions typed and synchronized).
It is recorded for proof-planning focus.
It is not proved as a meta-theorem and may change if the operator realization or transfer model is revised.

\paragraph{What remains unresolved even if the repair target is proved.}
Even with that neutralizing result, Stage~6 would still require separate closure of:
\begin{enumerate}
  \item no-new-off-line-branch emergence outside transfer-reachable classes;
  \item the no-alternative-locus theorem target for all of $\mathcal{B}$ on $\mathcal{A}_{\mathrm{strip}}$;
  \item the master Stage~6 exclusion theorem that upgrades local control to full-strip exclusion under one synchronized package.
\end{enumerate}

\subsection*{Interpretation of intermediate evidence}
Computational checks, model examples, and heuristic consistency tests are useful for stress-testing definitions and detecting contradictions, but they are not substitutes for proof.
They may justify further investigation; they do not discharge formal obligations.

\subsection*{Policy for unresolved steps}
Any unresolved dependency should be treated as open and cited where it is used.
No conclusion stronger than the proved dependencies is warranted.
Accordingly, the manuscript should be read as materials for mathematical audit of a proposed proof framework, with explicit open bridges rather than implicit assumptions.
