This section separates established inputs from draft theorem targets.

\subsection*{Established inputs (from standard references)}
\begin{proposition}[Functional symmetry]
\label{prop:functional-symmetry}
The completed zeta function
\[
\xi(s)=\tfrac12 s(s-1)\pi^{-s/2}\Gamma\!\left(\tfrac{s}{2}\right)\zeta(s)
\]
satisfies $\xi(s)=\xi(1-s)$; see \cite{Riemann1859,Edwards1974,Titchmarsh1986}.
\end{proposition}

\begin{proposition}[Zero-set symmetries]
\label{prop:zero-symmetries}
If $\rho$ is a nontrivial zero of $\zeta$, then $1-\rho$ and $\overline{\rho}$ are also nontrivial zeros; see \cite{Edwards1974,Titchmarsh1986}.
\end{proposition}

\subsection*{Draft theorem targets (not proved in this manuscript version)}
\begin{drafttheorem}[Target A: zero--balance correspondence]
\label{thm:target-correspondence}
\placeholder{Theorem target under construction; proof not yet provided.}
Target statement (conditional): once the manuscript definitions of $H$ and the balance criterion are finalized, one aims to prove that nontrivial zeros in the critical strip correspond exactly to balanced points.
The target is conditioned on a declared operator-theoretic support package and analytic-control assumptions sufficient to make the correspondence non-circular and theorem-usable.
\end{drafttheorem}

\begin{drafttheorem}[Target B: critical-line localization and no-alternative-locus target]
\label{thm:target-uniqueness}
\placeholder{Theorem target under construction; proof not yet provided.}
Target statement (conditional; theorem target only): let $\mathcal{A}$ be the admissible class and let
\[
\mathcal{B}:=\{s\in\mathcal{A}:\Phi_H(s)=0\}
\]
denote the balanced set under a finalized $H/\Phi_H$ package.
Under an explicit hypothesis set $\mathcal{H}_B$ (admissibility synchronization, operator-theoretic support, symmetry compatibility, and analytic-control/rigidity ingredients), one aims to prove:
\begin{enumerate}
  \item \textbf{Local critical-line uniqueness target:} every balanced point in the local regime $\mathcal{R}_{\mathrm{loc}}\subseteq\mathcal{A}$ covered by $\mathcal{H}_B$ satisfies $\RePart(s)=\tfrac12$.
  \item \textbf{Local-to-global transfer target (closure bridge):} there exists a theorem-level extension principle, stated under an explicit synchronized hypothesis package $\mathcal{H}_{\mathrm{tr}}$, that transports the Stage-5 local uniqueness conclusion from $\mathcal{R}_{\mathrm{loc}}$ to all regimes used in the reduction.
  Here ``local'' means the Stage-5 regime $\mathcal{R}_{\mathrm{loc}}\subseteq\mathcal{A}_{\mathrm{strip}}$ where uniqueness estimates are proved/assumed, while ``global'' means the full admissible strip class $\mathcal{A}_{\mathrm{strip}}$.
  The transfer target must explicitly control boundary-near, non-perturbative, and large-parameter regions in
  \[
  \mathcal{A}_{\mathrm{strip}}:=\{s\in\mathcal{A}:0<\RePart(s)<1\},
  \]
  and must exclude hidden off-line balanced branches that could appear only outside $\mathcal{R}_{\mathrm{loc}}$.
  In theorem-target form, the bridge must provide:
  \[
  \Big(\forall s\in\mathcal{B}\cap\mathcal{R}_{\mathrm{loc}},\ \RePart(s)=\tfrac12\Big)\ \Longrightarrow\
  \Big(\forall s\in\mathcal{B}\cap\mathcal{A}_{\mathrm{strip}},\ \RePart(s)=\tfrac12\Big),
  \]
  under one synchronized package $\mathcal{H}_{\mathrm{tr}}$ compatible with Target~A, local Target~B, and Stage~6.
  \item \textbf{Global no-alternative-locus target:} in the full admissible strip class
  \[
  \mathcal{A}_{\mathrm{strip}}:=\{s\in\mathcal{A}:0<\RePart(s)<1\},
  \]
  every balanced point satisfies $\RePart(s)=\tfrac12$.
  Equivalently, the theorem target excludes all off-line balance-supporting loci in $\mathcal{A}_{\mathrm{strip}}$, including:
  \begin{enumerate}
    \item alternative vertical lines $\RePart(s)=\sigma_0\neq\tfrac12$;
    \item non-vertical curves or higher-dimensional submanifolds carrying $\Phi_H=0$;
    \item disconnected off-line balanced components;
    \item regime-specific off-line loci that may appear only outside $\mathcal{R}_{\mathrm{loc}}$ unless globally excluded.
  \end{enumerate}
  \item \textbf{Contradiction compatibility target:} any assumed off-line balanced point $s_\ast\in\mathcal{A}_{\mathrm{strip}}$ with $\RePart(s_\ast)\neq\tfrac12$ must contradict at least one ingredient of the same synchronized hypothesis package used for local uniqueness, transfer, and global exclusion.
\end{enumerate}
Equivalent formulation target:
\[
\mathcal{B}=\mathcal{A}\cap\{s:\RePart(s)=\tfrac12\}.
\]
This manuscript version does not prove the above statement.
\end{drafttheorem}

\begin{remark}[What a no-alternative-locus theorem target must assume]
Target~B requires more than reflection symmetry.
Symmetry can imply pairings such as $s\leftrightarrow 1-s$ without ruling out off-line balanced pairs.
Therefore a valid proof target must state hypotheses strong enough to exclude alternative loci.
At minimum, one must specify:
\begin{enumerate}
  \item \textbf{Admissibility synchronization:} the same admissible class for Target~A, local Target~B, and Stage~6 exclusion transfer.
  \item \textbf{Symmetry compatibility:} reflection/conjugation transport preserves admissibility and theorem hypotheses.
  \item \textbf{Global control ingredient(s):} explicit coercivity, positivity, rigidity, monotonicity, or equivalent structure ruling out off-line exact balance.
  \item \textbf{Analytic-control closure:} assumptions preventing hidden off-line branches created by loss of compactness, boundary singular behavior, or regime changes outside local uniqueness.
\end{enumerate}
\end{remark}

\begin{remark}[Failure patterns that remain insufficient for Target~B]
The following argument forms are insufficient on their own:
\begin{enumerate}
  \item regime-restricted proofs that only treat perturbative neighborhoods,
  \item axis-symmetry statements for $\mathcal{B}$ without axis-uniqueness,
  \item exclusion arguments whose hypotheses are not inherited by the correspondence class from Target~A.
\end{enumerate}
\end{remark}

\begin{conjecture}[RH reduction under targets A and B]
Conditional implication only: if Targets~A and~B are both proved with a compatible set of explicit assumptions and definitions, then every nontrivial zero is balanced (Target~A) and every balanced point lies on $\RePart(s)=\tfrac12$ (Target~B), so RH follows under those proved hypotheses.
\end{conjecture}
