We record the logical dependency chain as a proof program for audit.  This section specifies required lemmas and bridges, but does not claim that those bridges are proved.

\subsection*{Program-level dependency graph}
\begin{enumerate}
    \item Formal setup and admissible objects
    \item Operator construction and operator-side regularity
    \item Balance functional well-posedness
    \item Zero--balance correspondence (Target A)
    \item Critical-line uniqueness of balanced points (Target B)
    \item Global off-line exclusion mechanism
    \item Final RH reduction inside the framework
\end{enumerate}

\subsection*{Stage 1: Formal setup and admissible class}
\textbf{Required inputs.}
Precise definitions of the state space $H$, admissible data class, and the balance criterion; explicit regularity, decay, and symmetry assumptions.

\textbf{Intended output.}
A fixed formal context in which all subsequent operators and functionals are well-typed (domain/codomain, topology, and admissibility constraints).

\textbf{Current status.}
\textbf{Established} as framework definitions (subject to local clarification edits as notation evolves).

\subsection*{Stage 2: Operator construction and operator-side regularity}
\textbf{Required inputs.}
Stage 1 definitions, plus a concrete operator construction rule and hypotheses needed for boundedness/closability/spectral meaning (as appropriate to the chosen operator model).
For audit, Stage~2 must supply an explicit operator-theoretic package (OP1--OP8 as recorded in \texttt{spectral-framework.tex}): ambient space/domain typing, closure control, symmetry-domain invariance, intertwining/covariance identities, spectral-legitimacy for every invoked spectral object, compatibility with $\Phi_H$, admissibility stability under operator-side transforms, and dependency-locked usage maps.
At this stage, analytic-control obligations are recorded but not discharged; they are deferred to Stage~6 as a separate theorem package.

\textbf{Intended output.}
A mathematically controlled operator layer: existence of the constructed operator(s), admissible action on $H$, and a traceable list of operator properties actually used later.

\textbf{Current status.}
\textbf{Partial}.  Core construction ideas are present, but several operator-regularity statements remain assumption-level and require formal proofs under explicit hypotheses.
\openbridge{Stage~2 remains open at the OP-package level: no finalized theorem stack yet proves OP1--OP8 under one synchronized operator model.}

\subsection*{Stage 3: Balance functional well-posedness}
\textbf{Required inputs.}
Stages 1--2, including regularity and operator-control bounds sufficient to define the balance functional on the intended class.

\textbf{Intended output.}
Well-posedness package: definition on a specified domain, finiteness, continuity/differentiability properties needed downstream, and invariance/covariance statements used in correspondence arguments.

\textbf{Current status.}
\textbf{Partial}.  The functional is specified at the formal level; full well-posedness proofs are not complete in all parameter regimes.

\subsection*{Stage 4: Zero--balance correspondence bridge (Target A)}
\textbf{Required inputs.}
Stage 3 well-posedness plus a precise matching rule between balanced configurations and zeros of $\zeta$ in the manuscript's encoding.

\textbf{Intended output.}
A bidirectional correspondence theorem (or clearly one-directional theorem plus separate converse):
\[
\text{balanced point} \Longleftrightarrow \text{encoded zeta zero},
\]
with all side conditions explicit.

\textbf{Current status.}
\textbf{Open bridge}.  Target A (\cref{thm:target-correspondence}) is not yet proved.
\openbridge{Requires a rigorous, hypothesis-complete map between the balance condition and the zero set of $\zeta$, including injectivity/surjectivity conditions and exclusion of spurious balanced states.}

\subsection*{Stage 5: Critical-line uniqueness bridge (Target B)}
\textbf{Required inputs.}
Stage 4 correspondence plus structural constraints sufficient to force balanced configurations onto $\Re(s)=\tfrac12$.

\textbf{Intended output.}
A theorem-level \emph{localization} statement, with explicit regime and assumptions:
\[
\Phi_H(s)=0 \Longrightarrow \Re(s)=\tfrac12
\]
for all admissible $s$ in the Stage-5 regime.
This stage is allowed to be local/regime-scoped, provided the scope is explicit.

\textbf{Current status.}
\textbf{Open bridge}.  Target B (\cref{thm:target-uniqueness}) remains unproved.
\openbridge{Requires a fully rigorous uniqueness-of-balance theorem target with explicit hypotheses, explicit regime of validity, and explicit non-spuriousness conditions for the balance predicate.}

\subsection*{Stage 6: Global off-line exclusion mechanism}
\textbf{Required inputs.}
Refined estimates or structural principles compatible with Stages 2--5, sufficient to upgrade local uniqueness logic to a global exclusion statement.
In this revision, the manuscript selects a \emph{preferred theorem path} rather than a flat list of equally weighted possibilities:
\[
\text{local Target-B uniqueness on }\mathcal{R}_{\mathrm{loc}}
\Longrightarrow
\text{local-to-global transfer for }\mathcal{B}
\Longrightarrow
\text{no-alternative-locus closure on }\mathcal{A}_{\mathrm{strip}}.
\]
This preferred path is a strategy choice under review, not a proved theorem chain.
Other mechanism classes (coercive gap, positivity/monotonicity, rigidity, reflection-incompatibility, and direct contradiction routes) remain in scope, but are organized as supporting ingredients or fallback routes relative to the preferred closure path.
In addition, Stage~6 now records a \emph{candidate contradiction route}: one assumes an admissible off-line balanced point under a synchronized package (admissibility, balance well-definedness, reflection/conjugation compatibility, and required regularity regime), then derives contradiction with one declared global-control ingredient under the same package.
Stage~6 now isolates a \emph{local-to-global transfer theorem target} as a separate bridge: under synchronized hypotheses, local Stage-5 uniqueness on $\mathcal{R}_{\mathrm{loc}}$ must extend to the full admissible strip $\mathcal{A}_{\mathrm{strip}}$ with explicit continuation/compactness/uniformity control and explicit prevention of hidden off-line branches outside $\mathcal{R}_{\mathrm{loc}}$.
Stage~6 also isolates a distinct \emph{no-alternative-locus theorem target} for the balanced set
\[
\mathcal{B}=\{s\in\mathcal{A}_{\mathrm{strip}}:\Phi_H(s)=0\},
\]
namely that no connected component of $\mathcal{B}$ is off the critical line.
This target is stronger than local uniqueness and must explicitly exclude alternative vertical lines, off-line curves/submanifolds, disconnected off-line components, and regime-specific off-line loci outside the local regime.
Stage~6 also isolates an \emph{analytic-control support package} as a separate open bridge. In audit form, this package must provide: (AC1) strip-wide growth/defect bounds; (AC2) uniform convergence on transfer-relevant sectors; (AC3) justified interchange operations; (AC4) continuation/extension control across regimes; (AC5) no-hidden-branch control for $\mathcal{B}$; and (AC6) compatibility of local estimates with strip-wide admissibility. These AC items are theorem targets only in the present manuscript.
Stage~6 additionally depends on operator-side transfer stability from Stage~2: admissibility preservation under the operator transformations actually used in continuation/transport arguments and explicit traceability of those transformations to proved OP lemmas.
For clarity of theorem formulation, Stage~6 is now parameterized by the minimum synchronized package $\mathcal{H}_{\mathrm{S6}}^{\min}$ (defined in \texttt{critical-line-argument.tex}): admissibility synchronization/stability, strip-wide well-posedness of $\Phi_H$, symmetry compatibility without hypothesis loss, operator-side structural control actually used by transfer (OP-focused), analytic-control transfer conditions (AC1--AC6), no-hidden-branch/no-alternative-locus input, and contradiction-route compatibility under the same assumptions.
This package is the minimum needed to \emph{state} the preferred Stage~6 route coherently.
It is not a sufficiency claim for proving Stage~6.
Stronger coercive/positivity/rigidity assumptions remain optional support packages unless explicitly promoted.
Stage~6 is now centered on one explicit endpoint: the master exclusion theorem target \cref{thm:stage6-master-exclusion-target} in \texttt{critical-line-argument.tex}.
All Stage~6 sub-burdens are organized as obligations that discharge this single theorem target.
Stage~6 now names a single first subtheorem proving target inside this preferred route:
\begin{quote}
\textbf{First Stage~6 draft theorem target (open; contradiction form):} \cref{thm:stage6-first-subtarget-admissibility}, which assumes an admissible transfer-reachable off-line balanced candidate $s_\ast\in\mathcal{B}\cap\mathcal{A}_{\mathrm{strip}}$ with $\RePart(s_\ast)\neq\tfrac12$ under $\mathcal{H}_{\mathrm{S6}}^{\min}$ and targets contradiction via no-drift transport of the Stage-5 hypothesis tuple along continuation classes.
\end{quote}
This target is selected as the first entry point because it is the earliest dependency required before global transfer and no-alternative-locus statements are theorem-usable.
The designation is strategic and audit-oriented; it is not a proof claim.

\paragraph{Stage~6 now starts from an explicit contradiction-style theorem statement.}
The Stage~6 proving flow begins from the statement form of \cref{thm:stage6-first-subtarget-admissibility} rather than from mechanism prose alone:
\begin{enumerate}
  \item \textbf{Contradiction premise:} assume $s_\ast\in\mathcal{B}\cap\mathcal{A}_{\mathrm{strip}}$ with $\RePart(s_\ast)\neq\tfrac12$, transfer-reachable from $\mathcal{R}_{\mathrm{loc}}$ via some $C_\ast\in\mathfrak{C}_{\mathrm{tr}}$, under one synchronized package $\mathcal{H}_{\mathrm{S6}}^{\min}$.
  \item \textbf{Intermediate support burden:} prove the transport bridge that preserves the exact Stage-5 local hypothesis tuple along $C_\ast$ without hypothesis drift.
  \item \textbf{Immediate theorem target conclusion:} derive contradiction with transported Stage-5 local uniqueness and conclude transfer-reachable exclusion
  \[
  \mathcal{B}_{\mathrm{tr}}\cap\{s\in\mathcal{A}_{\mathrm{strip}}:\RePart(s)\neq\tfrac12\}=\varnothing.
  \]
\end{enumerate}
This is a theorem-target starting point only; it is not a proved Stage~6 result.
For dependency clarity, the intended theorem flow is:
\[
\underbrace{\text{first concrete analytic quantity }\Delta_{\mathrm{nd}}(C;\Theta_{\mathrm{S5}},\delta):=\sup_{u\in U(C)}d_{\Theta}^{(C)}(u)}_{\text{provisional no-drift defect functional (open)}}
\Longrightarrow
\underbrace{\text{initialization target \cref{lem:b4-delta-initialization-seed}}}_{\text{seed-anchor zero-defect base case on }\mathcal{R}_{\mathrm{loc}}\text{ (open)}}
\Longrightarrow
\underbrace{\text{primary structural-property lemma target \cref{lem:b4-delta-structural-nonincrease}}}_{\text{non-increase of }\Delta_{\mathrm{nd}}\text{ under synchronized extension (open)}}
\Longrightarrow
\underbrace{\text{first control lemma target }\cref{lem:b4-first-delta-control}\text{ for }\Delta_{\mathrm{nd}}}_{\text{precise classwise control statement on }\mathfrak{C}_{\mathrm{tr}}^{\mathrm{ctr}}\text{ (open)}}
\Longrightarrow
\underbrace{\text{no-drift lemma target \cref{lem:stage6-first-concrete-no-drift}/\cref{lem:b4-admissibility-stability-transfer}}}_{\text{transport-form persistence of the Stage-5 tuple (open)}}
\Longrightarrow
\underbrace{\text{neutralizing theorem target \cref{thm:stage6-neutralizing-transport-uniformity}}}_{\text{open contradiction enabler}}
\]
This subflow is the current Stage~6 proving spine for the no-drift checkpoint.
It is downstream of the contradiction-ready target \cref{thm:stage6-first-subtarget-admissibility} and upstream of later no-alternative-locus and master-exclusion burdens:
\[
\Longrightarrow
\underbrace{\text{resumed preferred Stage~6 route: no-new-off-line-branch}\ \Rightarrow\ \text{no-alternative-locus}\ \Rightarrow\ \text{master exclusion}}_{\text{still-open downstream obligations}}.
\]
The middle implication is an independent theorem target, not an automatic corollary of Stage~5.


\paragraph{First executable Stage~6 proof pattern (initialization $+$ non-increase $\Rightarrow$ first control; outline only).}
For audit-facing proof planning, the first intended derivation pattern is now fixed as:
\begin{enumerate}
  \item \textbf{Seed step (initialization target).} Choose a local anchor $a\in\mathcal{R}_{\mathrm{loc}}$ and its declared seed object $C_a^{\mathrm{seed}}\in\mathfrak{C}_{\mathrm{tr}}^{\mathrm{ctr}}$. Use \cref{lem:b4-delta-initialization-seed} to target
  \[
  \Delta_{\mathrm{nd}}(C_a^{\mathrm{seed}};\Theta_{\mathrm{S5}},\delta)=0.
  \]
  \item \textbf{Propagation step (structural non-increase target).} For any contradiction-relevant $C\in\mathfrak{C}_{\mathrm{tr}}^{\mathrm{ctr}}$ covered by synchronized seed-extension, apply \cref{lem:b4-delta-structural-nonincrease} along
  \(C_a^{\mathrm{seed}}\preceq C\) to target
  \[
  \Delta_{\mathrm{nd}}(C;\Theta_{\mathrm{S5}},\delta)
  \le
  \Delta_{\mathrm{nd}}(C_a^{\mathrm{seed}};\Theta_{\mathrm{S5}},\delta).
  \]
  \item \textbf{First control conclusion target.} Combine the two displays to obtain the classwise target
  \(
  \Delta_{\mathrm{nd}}(C;\Theta_{\mathrm{S5}},\delta)=0
  \)
  on $\mathfrak{C}_{\mathrm{tr}}^{\mathrm{ctr}}$, i.e. the target shape of \cref{lem:b4-first-delta-control}.
\end{enumerate}
This is an outline of intended derivation structure only.
It is not a completed derivation and does not assert proof of initialization, structural non-increase, or seed-extension coverage.


\paragraph{Primary structural-property lemma under audit for \texorpdfstring{$\Delta_{\mathrm{nd}}$}{Delta\_nd} control (status: open target).}
Inside the Stage~6 chain above, the manuscript now prioritizes one provisional lemma target,
\cref{lem:b4-delta-structural-nonincrease}, asserting:
non-increase of $\Delta_{\mathrm{nd}}$ under synchronized transport extension under one package $\mathcal{H}_{\mathrm{S6}}^{\min}$,
\[
C_1\preceq C_2\Longrightarrow
\Delta_{\mathrm{nd}}(C_2;\Theta_{\mathrm{S5}},\delta)
\le
\Delta_{\mathrm{nd}}(C_1;\Theta_{\mathrm{S5}},\delta).
\]
This target is prioritized because it directly supports the first control target (classwise vanishing on $\mathfrak{C}_{\mathrm{tr}}^{\mathrm{ctr}}$) once paired with the seed-anchor initialization target \cref{lem:b4-delta-initialization-seed} and seed-extension coverage, and it matches the current OP/AC interface without selecting a finalized operator realization.
It is not proved, not claimed final, and not claimed sufficient by itself.

\paragraph{Dependency orientation for the current first Stage~6 proving attempt.}
To sharpen technical focus, the manuscript classifies the current neutralizing step as
\emph{genuinely mixed with analytic dominant burden}.
In dependency-flow terms:
\begin{enumerate}
  \item \textbf{Dominant burden (analytic):} AC1--AC6 carry the primary load for no-drift transport from $\mathcal{R}_{\mathrm{loc}}$ to transfer-reachable points in $\mathcal{A}_{\mathrm{strip}}$.
  \item \textbf{Supporting burden (operator):} OP7--OP8 (with invoked OP1--OP6) keep transport and symmetry/admissibility clauses theorem-typed under the same package.
  \item \textbf{Neutralizing-result role:} \cref{thm:stage6-neutralizing-transport-uniformity} is the current bridge where these two burdens are synchronized for contradiction use.
\end{enumerate}
This orientation is a planning judgment for the present manuscript state.
It does not assert theorem-level dominance beyond the current route under audit.

\paragraph{Lemma stack attached to the first Stage~6 draft theorem target (all open).}
The initial proving attempt is explicitly scoped to the following stack in \texttt{lemmas.tex}:
\[
\cref{lem:b4-delta-initialization-seed}
\Rightarrow
\cref{lem:b4-delta-structural-nonincrease}
\Rightarrow
\cref{lem:b4-first-delta-control}
\Rightarrow
\cref{lem:b4-admissibility-stability-transfer}
\Rightarrow
\cref{lem:b4-neutralizing-transport-uniformity},
\]
with operator-side support from OP7--OP8 (and invoked OP1--OP6) and analytic-control support from AC1--AC6.
The no-new-off-line-branch, no-alternative-locus, and global-extension burdens are subsequent Stage~6 obligations, not part of this first no-drift subchain.
This separation is enforced for audit clarity and theorem-status discipline.


\paragraph{Single highest-risk dependency inside the first contradiction setup.}
Within the first contradiction-style Stage~6 target, the present highest-risk dependency is the no-drift transport step, now expressed through the provisional analytic defect quantity $\Delta_{\mathrm{nd}}(C;\Theta_{\mathrm{S5}},\delta)=\sup_{u\in U(C)}d_{\Theta}^{(C)}(u)$ on $\mathfrak{C}_{\mathrm{tr}}$.
The first concrete control target addressing that step is \cref{lem:b4-first-delta-control}, which aims to force classwise vanishing of this defect on the contradiction-relevant transfer subclass $\mathfrak{C}_{\mathrm{tr}}^{\mathrm{ctr}}$ under the same package $\mathcal{H}_{\mathrm{S6}}^{\min}$.
The first transport-form lemma target is then \cref{lem:stage6-first-concrete-no-drift} (ledger-aligned with \cref{lem:b4-admissibility-stability-transfer}), which rephrases that control as endpoint-usable Stage-5 tuple persistence along $\mathfrak{C}_{\mathrm{tr}}$.
If this bridge fails or remains underjustified, the contradiction step is not yet well-typed: Stage-5 uniqueness is invoked at the endpoint without a theorem-level no-drift transfer justification.
Accordingly, this bridge is the first proof-critical audit checkpoint in the Stage~6 dependency chain.
The manuscript now names one best candidate neutralizing theorem target for this checkpoint:
\cref{thm:stage6-neutralizing-transport-uniformity} in \texttt{critical-line-argument.tex}.
That target is explicitly open and is downstream of the first control lemma $\cref{lem:b4-first-delta-control}$ and its transport reformulation $\cref{lem:b4-admissibility-stability-transfer}$.
It is intended to repair only this no-drift contradiction-typing failure point, after which the route resumes with no-new-off-line-branch and no-alternative-locus burdens toward the master Stage~6 theorem.

\textbf{Intended output.}
A global theorem-level exclusion mechanism distinct from Stage 5, culminating in the master theorem target \cref{thm:stage6-master-exclusion-target}:
\begin{enumerate}
  \item \textbf{Master Stage~6 theorem target (endpoint):} full-strip exclusion of admissible off-line balanced configurations under $\mathcal{H}_{\mathrm{S6}}^{\min}$, tracked in aligned pointwise, set-theoretic, component/locus, and contradiction-style formulations.
  \item \textbf{Primary bridge burden:} theorem-level transfer from Stage-5 local uniqueness on $\mathcal{R}_{\mathrm{loc}}$ to full-strip control on $\mathcal{A}_{\mathrm{strip}}$, supported by AC1--AC6.
  \item \textbf{Primary no-alternative-locus burden:} theorem-level exclusion of off-line connected components of $\mathcal{B}$ on the full admissible strip.
  \item \textbf{Supporting mechanism burden:} coercive/positivity/rigidity ingredients strong enough to prove items (2)--(3) under synchronized assumptions.
  \item \textbf{Fallback burden:} reflection-incompatibility or direct contradiction-route closure if the primary transfer/no-alternative-locus path cannot be completed.
\end{enumerate}

\textbf{Current status.}
\textbf{Open}.  A mechanism template is now explicit, but no model-specific exclusion theorem is proved.
\openbridge{Requires a proved local-to-global transfer theorem target for $\mathcal{B}$ (or equivalent closure bridge), a proved analytic-control package AC1--AC6 (growth, uniformity, interchange legitimacy, continuation/compactness control, no-hidden-branch closure, and strip-admissibility compatibility), proof-quality global control including boundary-near and large-parameter regimes, and an explicit contradiction theorem from admissible off-line balance under one synchronized hypothesis package; computational checks may guide conjecture but do not substitute for the exclusion proof.}

\subsection*{Stage 7: Final RH reduction inside the framework}
\textbf{Required inputs.}
Completed Stages 4--6 with hypotheses synchronized and no circular dependencies.

\textbf{Intended output.}
A clean conditional reduction:
\begin{quote}
If Target A and Target B (with the global exclusion package) hold under assumptions $\mathcal{A}$, then RH follows within this framework.
\end{quote}

\textbf{Current status.}
\textbf{Open/conditional}.  Reduction logic is straightforward once bridges are proved, but present manuscript status is conditional on unresolved bridges.

\begin{remark}
Audit interpretation: failure of any open bridge (Stages 4--6) blocks the RH reduction.  This section is a dependency map for review, not a claim that those bridges are complete.
\end{remark}
